User-level Grid Monitoring with Inca 2

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
minor corrections - perhaps the last!
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6665 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a Java Swing GUI that an
Inca administrator uses to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles the implementation
(as described in the next section).  The Inca administrator can reload the
configuration at any point and make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories, and incat loads and displays the reporters
available from them (Figure~\ref{incat_fig}).
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The reports that a reporter produces on a
resource when executed with specific set of input arguments and runtime
environment are known as a \emph{report series} (or \emph{series} for short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful in determining interoperability
among Grids or whether an application's requirements are being
fulfilled on a Grid.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the database schema is
tuned to minimize redundant data.  Inca administrators can specify comparison
tests to run on reports as they are received, and the depot will send email
when the results of these comparisons change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

Data can be queried using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented using Java.

@@

To provide for security, all Inca components communicate with each other using
SSL, and sensitive information is encrypted before being stored to disk.  To
handle reporters that
require a proxy credential to execute, the reporter manager fetches a
short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
administrator), then destroys the proxy once the reporter has completed.
MyProxy authentication information is fetched from the agent each time a proxy
credential is needed and then cleared from memory.  Generating short-term 
proxies as needed is more secure than maintaining long-term
credentials and is easier to manage.

\SubSection{Scalability}

@@

A planned extension to Inca 2 supports the distribution of control and storage
workload among multiple Inca components.  Figure~\ref{tg_coord_fig} shows a
scenario where two Inca deployments coordinate with each other.  This could
occur in application communities like GEON~\cite{geon}, which maintains its
own Grid but also has access to TeraGrid resources.   Running two Inca
deployments independently could result in duplicate testing.  Instead, we plan
to eliminate redundancy by allowing multiple deployments to coordinate suite
execution.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.

@@

Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across their 11 heterogeneous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.

@@

In order to improve problem detection and diagnosis for system administrators,
we plan to add graph rendering and statistical
analysis capabilities to the Inca data consumer.  This will improve troubleshooting capabilities by
allowing errors to be understood in a historical context.  It will also enable
summary displays analogous to those generated by Web page statistics packages
like Webalizer~\cite{webalizer} that provide a number of useful "Top"
statistics.  We expect to follow recommendations from TeraGrid and other Inca
users on the types of statistics and graphs that will prove to be most useful.
Our plan is to offer a default set of statistics and graphs that can be used
directly and to provide the capability to add others.

Also to aid system administrator troubleshooting,
we plan to enhance Inca with a knowledge base that can be used to
suggest solutions to problems (or point to known bugs if there is no solution
available).  The knowledge base would be populated by solutions provided by
system administrators -- the content would be self-moderated in order to
improve its quality (by voting or adding comments to each other's
contributions).  A knowledge base could provide a potentially vital resource
for system administrators and offer a forum for sharing
invaluable experience and skills.

@@

This work was supported by the following NSF grants:  Cooperative Agreement
Award \#0503944 SCI: TeraGrid Resource Partners,

>>>>

% Incat is interface Inca admin uses to configure reporters to resources
% introduce series here; why suites are important It is designed to make the
% effort of configuring and maintaining 100s series on resources easilty
The Inca administrative tool (incat) is a Java Swing GUI that
Inca administrators use to configure user-level Grid monitoring on their
resources.  Incat allows an Inca administrator to choose which resources to
monitor and which reporters to deploy to those resources.  The configuration
is stored in a XML file and sent to the agent, which handles its implementation
(described in the next section).  The Inca administrator can reload the
configuration to make updates.  Incat provides a number of
conveniences that enable a large number of results to be managed and collected
with a minimum effort.

To begin reporter configuration, the Inca administrator enters the location of
one more reporter repositories, and incat loads and displays the reporters
available from them (Figure~\ref{incat_fig}).
For each reporter, the Inca administrator can specify the resources to run on,
input arguments, the runtime environment, the frequency of execution, resource
limits, and email notifications.  The sequence of reports that a reporter
produces on a resource when executed with a specific set of input arguments and
runtime environment is known as a \emph{report series} (or \emph{series} for
short).
Thus, the grid.globus.gramPing reporter in Figure~\ref{pingReporter} would
produce one report series when executed with 'blue.ufo.edu' as the host argument and another report series with 'red.ufo.edu'.  A set of related
series can be grouped into \emph{suites} and shared across other Inca
deployments, e.g.,  a Globus suite or a data transfer
performance suite.  Suites can also be useful in determining interoperability
among Grids or whether an application's requirements are being
fulfilled on a Grid.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the database schema is
tuned to minimize redundant data.  Inca administrators can specify pattern
tests to run on reports as they are received, and the depot will send email
when the results of these tests change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

Data can be retrieved using SQL queries. Predefined queries exist to return the
latest report instances of a suite, a single report instance, or a report
history.  A Web services interface is also available to provide
unauthenticated query access to data.  The depot is implemented using Java.

@@

To provide for security, all Inca components communicate with each other using
SSL, and sensitive information is encrypted before being written to disk.  To
handle reporters that
require a proxy credential to execute, the reporter manager fetches a
short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
administrator), then destroys the proxy once the reporter has completed.
MyProxy authentication information is fetched from the agent each time a proxy
credential is needed and then cleared from memory.  Generating short-term 
proxies as needed is more secure than maintaining long-term
credentials and is easier to manage.

\SubSection{Coordinating Inca Deployments}

@@

A planned extension to Inca 2 supports the distribution of control and storage
workload among multiple Inca components.  Figure~\ref{tg_coord_fig} shows a
scenario where two Inca deployments coordinate with each other.  This could
occur in application communities like GEON~\cite{geon}, which maintains its
own Grid but also has access to TeraGrid resources.   Running two Inca
deployments independently could result in duplicate testing.  Instead, we plan
to eliminate redundancy by allowing multiple deployments to coordinate suite
execution.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  This extension is also expected
to provide the mechanisms for scalability and fault tolerance in the Inca
system.

@@

Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005, respectively.  
Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across 11 heterogeneous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.

@@

In order to improve problem detection and diagnosis for system administrators,
we plan to add graph rendering and statistical
analysis capabilities to the Inca data consumer.  This will improve troubleshooting capabilities by
allowing errors to be understood in a historical context.  It will also enable
summary displays analogous to those generated by Web page statistics packages
like Webalizer~\cite{webalizer} that provide a number of useful
statistics.  We expect to follow recommendations from TeraGrid and other Inca
users on the types of statistics and graphs that will be most useful.
Our plan is to offer a default set of statistics and graphs that can be used
directly and to provide the capability to add others.

Also to aid system administrator troubleshooting,
we plan to enhance Inca with a knowledge base that can be used to
discuss problems and suggest solutions.
The knowledge base will be populated by solutions provided by
system administrators and self-moderated to
improve quality.
This knowledge base could provide a vital resource
for system administrators and offer a forum for sharing
valuable experience and skills.

@@

The authors would like to thank Denis Girou and David Spence for providing
details for the DEISA and NGS Inca deployments, respectively.  This work was
supported by NSF grants SCI-0503944, SCI-0438741, and SCI-0503697.
